Opening up the court (surface) in tennis grand slams

### 2018-09-16 contest/surface-type/paper-tennis.Rmd
now using library!

## To change into library(courtsports)
devtools::load_all("../..")

@@

step_model_n <- model_individual(player_name = "Rafael Nadal", data = gs_partial_players)

@@

step_model_f <- model_individual(player_name = "Roger Federer", data = gs_partial_players, ref = "Wimbledon")

@@

step_model_w <- model_individual(player_name = "Serena Williams", data = gs_partial_players,
                                 start_lower = TRUE, ref = "Australian Open")

>>>>

## To change into library(courtsports)
library(courtsports)

@@

step_model_n <- courtsports:::model_individual(player_name = "Rafael Nadal", data = gs_partial_players)

@@

step_model_f <- courtsports:::model_individual(player_name = "Roger Federer", data = gs_partial_players, ref = "Wimbledon")

@@

step_model_w <- courtsports:::model_individual(player_name = "Serena Williams", data = gs_partial_players,
                                 start_lower = TRUE, ref = "Australian Open")
